Analyzing Performance Bottleneck in Graph Neural Network Training: An Experimental View

### 2020-08-22 Manuscript/sec2-review-of-graph-neural-network.tex
更新论文稿。

\begin{figure}
    \centering
    \subfloat[Neighbor sampling\label{fig:gnn_sampling_neighbor_sampling}]{\includegraphics[height=4cm]{figs/illustration/layer_sampling.pdf}}
    %
    \subfloat[Graph sampling\label{fig:gnn_sampling_graph_sampling}]{\includegraphics[height=4cm]{figs/illustration/graph_sampling.pdf}}
    \caption{Training a GNN with sampling techniques. The faded graph neurons and their connections are inactivated.}
    \label{fig:gnn_sampling}
\end{figure}

>>>>

\begin{figure}
    \centering
    \subfloat[Neighbor sampling\label{fig:gnn_sampling_neighbor_sampling}]{\includegraphics[height=4.1cm]{figs/illustration/layer_sampling.pdf}}
    %
    \subfloat[Graph sampling\label{fig:gnn_sampling_graph_sampling}]{\includegraphics[height=4.1cm]{figs/illustration/graph_sampling.pdf}}
    \caption{Training a GNN with sampling techniques. The faded graph neurons and their connections are inactivated.}
    \label{fig:gnn_sampling}
\end{figure}
